Formalizing Stack Safety as a Security Property

### 2021-07-07 submission3/main.tex
Nit in 2

The key intuition is that to be considered as having returned to {\tt main}, {\tt f} needs
to do more than just execute a return-labeled instruction: it must actually reach the
appropriate return target in {\tt main}.
We add a new piece of context to our diagram: we keep a stack of return targets, and a callee is
only considered to have returned when it reaches a state that matches the caller's target.
A return target is associated with a set of sealed locations that will become unsealed
when it is reached, here represented by sharing a color with the sealed data.

>>>>

The key intuition is that to be considered as having returned to {\tt main}, {\tt f} needs
to do more than just execute a return-labeled instruction: it must actually reach the
appropriate return target in {\tt main}.
We add a new piece of context to our diagram: we keep a stack of return targets, and a callee is
only considered to have returned when it reaches a state that matches the caller's target.
A return target is associated with a set of sealed locations that will become unsealed
when it is reached, represented here by sharing a color with the sealed data.
